{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {User Manual for TersectBrowser+}

### 2025-05-05 UserManual/UserMan.tex
Added barcode generation transcript

4. Barcode generation

>>>>

4. Barcode generation
Once the user has identified an accession and a bin of interest, TersectBrowser+ offers the capability to generate accession-specific barcodes for that interval. Clicking on a specific bin opens a popup menu with a `Create barcode' button. Clicking this button opens a larger Barcode Generator popup window, where the user can specify barcode size and the maximum number of variants per barcode, which are populated with the default values on 150 and 1 respectively. Clicking on the `Generate' button will create the barcodes, and a `Download' button will appear. Clicking the `Download' button automatically downloads a .tsv file containing the generated barcodes and their associated statistics.
